Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-10 manuscript.tex
2.2

\subsubsection{Extension to traveling waves}
%: >>>>>>>> Laurent is here <<<<<<<<<<<<<<
TODO :~\citep{bringuier_horizontal_1999} latency basin

>>>>

\subsection{Extension to traveling waves}
%: >>>>>>>> Laurent is here <<<<<<<<<<<<<<
To further investigate the role of precise timing , let us also focus on the role of differential timings across nervous. As we have seen, a visual feature will induce the firing of different cells at different latencies~\citep{celebrini_dynamics_1993}. Using intra-cellular recordings, it was shown that the response to a focal visual activation would elicit a latency basin, that is a graded onset of the neural response~\citep{bringuier_horizontal_1999}. In particular, it was shown that the network of horizontal connections within a cortical area is typically not myelinated and that this latency basin would be determined by the propagation speed within the area. For generic visual scenes, this processes would generate an interplay between the dynamics of the sensory signal and the spatio- temporal determinants of these interactions.
